Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-01-09 Ben_Manuscripts/structure_paper/supplemental.tex
Added new figures

		\item 2.5 \AA~: The smallest pore radius that we can achieve before energy 
		minimization becomes problematic is 2.5 \AA.

		\item 5 \AA~:

		\item 8 \AA~: The largest pore radius that can achieve before energy minimization
		becomes problematic is 8 \AA.
	  \end{enumerate}

	  \begin{table}[h]
	  \centering
	  \begin{tabular}{cc}
	  \toprule
	  Initial Pore Radius & Equilibrated Pore Radius \\
	  \midrule
	  % BJC: to be updated once simulations are run out long enough
	  2.5 \AA & $0.394 \pm 0.002$ \AA \\
	  5 \AA   & $0.423 \pm 0.002$ \AA \\ % final result
	  8 \AA   & $0.721 \pm 0.002$ \AA \\
	  \bottomrule
	  \end{tabular}
	  \caption{Caption of the future!}~\label{table:radii}
	  \end{table}

>>>>

		\item 2.5 \AA~: The smallest pore radius that we can achieve
		before energy minimization becomes problematic is 2.5 \AA. After being run
		through the full dry equilibration procedure, the average pore radius is 0.40
		$\pm$ 0.01 \AA.

		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
		slightly larger than the equilibrated pore radius of the system simulated with
		an intial pore radius of 2.5 \AA. After being run through the full dry
		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
		agrees with the 2.5 \AA~ configuration within error.

		\item 8 \AA~: The largest pore radius that can achieved before
		energy minimization becomes problematic is 8 \AA. One should use caution with
		such a structure because of the relatively large vacuum space that is created
		in the pore region of the initial configuration. After being run through the
		full dry equilibration procedure, we see a combination of cylindrical and
		slit-like pores (Figure~\ref{fig:slits}). We are wary of such a non-symmetric
		structure and choose not to use a pore radius of 8 \AA for our starting configurations.

	  \begin{table}[h]
	  \centering
	  \begin{tabular}{cc}
	  \toprule
	  Initial Pore Radius & Equilibrated Pore Radius \\
	  \midrule
	  % BJC: to be updated once simulations are run out long enough
	  2.5 \AA & $0.40 \pm 0.01$ \AA \\
	  5 \AA   & $0.42 \pm 0.01$ \AA \\ % final result
	  8 \AA   & $0.69 \pm 0.01$ \AA \\
	  \bottomrule
	  \end{tabular}
	  \caption{The average pore radii of systems built with an initial pore
		  radius of 2.5 \AA~and 5 \AA~equilibrate to values that agree within error. If
		  the pore radius is too large, slit pores may form.}~\label{table:radii}
	  \end{table}

	  \begin{figure}
	  \centering
          \includegraphics[width=\textwidth]{slit_pores.png}
	  \caption{A system that was built with an initial pore radius of 8
		  \AA~equilibrates to a structure that exhibits both cylindrical and slit-like
		  pores. As pictured here, sodium ions are colored blue, carbon atoms in the
		  aromatic ring of the head group are colored orange and all else is colored
		  cyan.}~\label{fig:slits}
	  \end{figure}
